---
title: Introducing biocViews
---

# Basic concepts

## Introduction to biocViews

"biocViews" is the name of a package in Bioconductor that performs many roles

- it was initially proposed to emulate [CRAN task views](https://cran.r-project.org/web/views/), but
did not achieve the levels of curation and narration present there
- it was implemented as an instance of Bioconductor's "graph" class
    - every vocabulary element is node in the biocViews graph
    - "is a" conceptual relationships are expressed using directed edges

Illustration using R:

```{r lkbc1, message=FALSE}
library(biocViews)
library(graph)
data(biocViewsVocab)
biocViewsVocab
head(nodes(biocViewsVocab),12)
head(edges(biocViewsVocab),3)
```

## Quick view of EDAM in R

The following has a one-time startup cost of introducing
infrastructure for working with owlready2 (python) in R.
```{r geted}
library(ontoProc) # must use Bioc 3.20
ed = setup_entities2("https://edamontology.org/EDAM_1.25.owl")
head(ed$name, 12)
onto_plot2(ed, names(ed$name[ed$children$format_1915]))
```
